Integrated farming and global warming mitigation in Brazil

### 2022-08-02 manuscript/manuscript.qmd
Write second paragraph of introduction.

>>>>

Unfortunately, estimates of carbon sequestration by ICLF at larger scales usually use point estimates, which can severely bias the results towards one direction. @Azevedo_2018 used a CO<sub>2</sub>-eq removal factor of -6.24 t CO<sub>2</sub>-eq ha<sup>-1</sup> y<sup>-1</sup>, which was extracted from one experiment comparing integrated crop-livestock (ICL) systems to pasture [@Carvalho_2010], and did not observe consistent differences between these types of systems. The removal factor was then extrapolated over estimated ILPF area, this simplification is the best guess that Brazil have over the potential of integrated systems in reducing liquid emissions. In face of such scenario, this study aims to generate estimations of CO<sub>2</sub>-eq removal accounting for variation in many aspects, soil attributes, ICLF system characteristics, species used, spacing and climate. We expect that such estimations will provide more realistic ranges of possible outcomes in a diverse set of future scenarios of ICLF expansion in Brazil.
